The SMT Competition 2015--2018

### 2019-04-14 2018/report/SMT-COMP.tex
Report: Pass over "Very quick solutions".

The time limits used in each year are relatively long (20 or 40 minutes) whereas some applications of SMT solvers (e.g. software verification) make use of very short time limits. We ask the question \emph{how would the \maintrack results change if we consider a much shorter time limit of 24 seconds?}\footnote{This time limit was inspired by a conversation with Liana Hadarean as it is a time limit being used in one application of SMT solvers in Amazon.}. We only consider the \maintrack here as this is the setting where short time limits are most likely to be relevant. The results of this analysis are given in Table~\ref{tab:results:24s}. As in the previous, this highlights the different winners under this new scheme only. Here we see STP winning a division for the first time in our analysis (QF\_BV in 2016) and Yices2 performing well.

>>>>

Different application domains of SMT typically impose a wide range of time
limits (from hours to seconds). In domains with very low time limits, these
limits are, in the incremental case, usually even defined per incremental
query.  With 20 and 40 minutes, the time limits used in the competition for all
tracks in all four years were relatively long and the same for all benchmarks,
thus agnostic to the application domain of a benchmark.  Hence, it is
interesting to investigate how the results change if we consider a much shorter
time limit.  Table~\ref{tab:results:24s} shows the results of virtually
imposing a time limit of 24 seconds\footnote{This time limit is used for the
new 24 seconds score introduced in SMT-COMP 2019 and was inspired by a use case
at Amazon.} in the \maintrack.  As in the previous, this highlights the
different winners under this new scheme only. Here we see STP winning a
division for the first time in our analysis (QF\_BV in 2016) and Yices2
performing well.

We only consider the \maintrack here, since for the other two tracks, the
results are less interesting.  In the \apptrack, for such low time limits we
are rather interested in a time limit per query, which we are unable to impose
on the existing data since it is not possible to extract wallclock run time
information per incremental query from the data of the competitions (as
mentioned above, StarExec does not record this information).  In the
\ucoretrack, the main focus is on producing small unsat-cores and solving times
are of secondary interest.  Additionally, benchmarks with known unsatisfiable
status from the \maintrack are used, and thus these results are already
available from the \maintrack analysis in Table~\ref{tab:results:24s}
(disregarding the fact that enabling unsat core production may slow down a
solver, depending on the technique).
